A Data-Driven Framework for Neural Field Modeling

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
fixed a couple of typos

Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can be substantial. The Euler method was used for its simplicity. The sampling period of 1~ms was used in this paper, which yielded a stable discrete-time system and good estimation results. An analysis of the error introduced by Euler discretization method can be found in~\citet{Butcher2008}. An alternative to Euler's method is the local linearization method~\citep{Ozaki1994}.

>>>>

Note, the discretization using the first order Euler method has the potential to affect the system's behaviour, where the difference between the continuous and discrete-time systems can potentially be substantial. The Euler method was used for its simplicity. The sampling period of 1~ms was used in this paper, which yielded a stable discrete-time system and good estimation results. An analysis of the error introduced by Euler discretization method can be found in~\citet{Butcher2008}. An alternative to Euler's method is the local linearization method~\citep{Ozaki1994}.
